Reading Notes

### 2020-07-29 2pd.tex
add todo notes

\subsection*{Objective 4: Analysis}
Use charge transfer, diffraction to tell which models are the best

>>>>

\subsection*{Objective 4: Analysis}
Use charge transfer, diffraction to tell which models are the best
<cite a bunch of experimental papers we can compare to>
<cite our papers that show we can do this comparison already>
